---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bbsubset

<!-- badges: start -->
<!-- badges: end -->

## What's this for ?

When you have or create a DNA barcode, the size is often larger than you want. 
`bbsubset` is a simple tool for R to select a subset of DNA barcodes from the fullset in terms of avoiding the sequence error.


## Installation

### Install the devtools package

To install `bbsubset`, start by installing the `devtools` package. The best way to do this is from CRAN with:

```r
install.packages("devtools")
```

### Install bbsubset

Install bbsubset from GitHub with devtools

``` r
devtools::install_github("tfwis/bbsubset")
```


## Input file

The fullset of DNA barcode is needed to be entered in vector class, and One element of a vector is one barcode.

```{r}
head(bbsubset::sample_barcodes)
```


## Wrokflow

**Step1: Preperation of the input file**  
**Step2: Selecet LP solver**  
**Step3: Extract subset by `bbsubset`**  


## Tutorial

#### Load packages

Please confirm that these packages are installed before trying this
example.

``` r
library(ROI)
library(slam)
```

#### Create barcode set by `DNABarcodes`

The DNA barcode sets created by `DNABarcodes` meets the requirement for input file descreibed above.  
Usage of `DNABarcodes` is [here](https://bioconductor.org/packages/release/bioc/vignettes/DNABarcodes/inst/doc/DNABarcodes.html)

``` {r}
barcodes <- DNABarcodes::create.dnabarcodes(n=6, dist=3)
```

### Select LP solver

`bbsubset` have tolerate to select LP solver via ROI.  
By default, solver is set to `lpsolve`. So if you want to run `bbsubset` by default, library `ROI.plugin.lpsolve`.

``` {r}
library(ROI.plugin.lpsolve)
```

### Extract subset

``` {r}
myset <- bbsubset::bbsubset(barcodes,12)
myset$subset
```

### Validate nucleotide balance

`bbsubset::basecomp()` enables to validate the nucleotide balance of the subset.  
Each Colum show the numebre of each 

``` {r}
bbsubset::basecomp(myset$subset)
```


## Option

### Set timeout

You can set a timeout. How to set the timeout depends on the solver, please check the API of each solver. In the following code, `lpsolve` is used.

``` {r}
myset <- bbsubset::bbsubset(barcodes,5,solver="lpsolve",timeout=10) 
```

### Subset extraction with other LP solver

Show the case of using other solver. (e.g. gurobi)

``` r
library(ROI.plugin.gurobi)
myset <- bbsubset::bbsubset(barcodes,12,Solver="gurobi")
bbsubset::basecomp(myset$subset)
#>   1bp 2bp 3bp 4bp 5bp 6bp
#> A   3   3   3   3   3   3
#> C   3   3   3   3   3   3
#> T   3   3   3   3   3   3
#> G   3   3   3   3   3   3
```
